Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-09-16 manuscript/paper-tycho.tex
1st round paper comments; average FWHM fit tables
Incorporate feedback from Rob/Brian into manuscript, restructure for
tables to be added.

% \documentclass[manuscript]{aastex}  % one-column, double-spaced
% \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
% \documentclass[iop, apj, numberedappendix]{emulateapj}

@@

\usepackage{amsmath}  % amsthm, amssymb
\usepackage{hyperref}
% \usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
\usepackage{booktabs}
%\usepackage[labelfont=bf, labelsep=period]{caption}  % Custom float captions
%\usepackage{pdflscape}  % rotate pages (Texlive)

\newcommand{\mt}{\mathrm}
\newcommand{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
\newcommand{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
\newcommand{\ptl}{\partial}
\newcommand{\del}{\nabla}

% This paper
\newcommand{\tsup}{\textsuperscript}
\newcommand{\Chandra}{\textit{Chandra}\ }
\defcitealias{ressler2014}{R14}

@@

\title{Energy Dependent X-Ray Rim Widths in Tycho's Supernova Remnant}

@@

\begin{abstract}
\note[Aaron]{Copy pasted from NASA abstract, not reviewed}
Young supernova remnants may exhibit thin (~1--10\% of shock radius) X-ray rims
of synchrotron radiation from forward shock-accelerated electrons that travel
downstream of the shock and quickly cease to radiate. Rim widths limited by
radiative energy losses should decrease with energy and require magnetic field
amplification $10$--$100\times$ that expected from adiabatic shock compression.
Damped magnetic fields behind rims may produce thin rims without strong field
amplification but require energy-independent rim widths. We measured rim widths
around Tycho's supernova remnant in 5 energy bands using a 750 ks \Chandra
observation. Rims narrow with increasing energy, favoring loss-limited
radiation over magnetic damping. Observed widths are best fit by electron
transport models requiring amplified magnetic fields $\abt0.1$--$1$ mG and
particle diffusion $\abt1$--$10\times$ Bohm values, consistent with prior work.
Inferred magnetic fields, diffusion coefficients, and diffusion-energy scaling
may constrain models for cosmic ray acceleration in supernova remnants and
plasma turbulence in astrophysical shocks.
\end{abstract}

@@

% -------------------
% Background / review
% -------------------
\subsection{What are thin rims?}

Define thin rims (hereafter, thin rims).
\note[Aaron]{most text below is copy-pasted from my own notes -- explanation
may be too simplistic}

Somewhere here, define upstream/downstream of shock (makes sense in reference
frame of shock).

Accelerating ISM/CSM particles in the forward shocks of supernovae emit
synchrotron radiation.  Emission is strong in the shock's immediate wake, but
dies off quickly downstream as particles radiate and lose energy. The radiation
from a spherical blast wave, then, is shell-like with bright X-ray and radio
rims/filaments due to line-of-sight projection.  These filaments have finite
and energy-dependent widths, set by:
(1) \emph{synchrotron losses}.  At the shock, high energy electrons efficiently
radiate harder x-ray photons.  As electrons are advected downstream while
radiating, they radiate at lower energies and lose energy more slowly.
Synchrotron losses depend on the initial electron energy distribution and the
gradual decrease of electron energies downstream of the shock.
(2) \emph{diffusion}.  Random motion with respect to bulk plasma advection.
Higher energy electrons diffuse and travel further downstream than would be
expected from pure advection; hence, higher energy radiation may be seen
farther downstream of the shock than expected. Higher energy particles may also
diffuse \emph{ahead} of the shock, possibly giving rise to a so-called
``cosmic-ray shock precursor''.  Note that this is distinct from radiative
precursors \citep[e.g.,][]{ghavamian2000}.

Mention relevance to: cosmic ray acceleration, turbulent field amplification,
(note assumptions in re proton/electron spectra).  Cut-off energy of injected
electrons?  Broadly, all astrophysical shock processes: AGN jets, galaxy
clusters \citep{van-weeren2010}, PWNe, et cetera.  Usual background,
utility spiel.

% ------------------------
% Measurements and meaning
% ------------------------
\subsection{Prior measurements and inferred physical parameters}

Models for particle transport.  Bohm, sub-Bohm diffusion.
Testable model predictions of magnetic damping \citep{pohl2005}.

Previous measurements of basic observables \citep[e.g.,][]{bamba2003,
bamba2005-hist, bamba2005-vela, parizot2006} and consequences.
Conclusion that magnetic fields are amplified.

Equivocal results by \citet{araya2010} for Cas A.
\citet{ressler2014} found rim narrowing in the remnant of SN 1006.

% -----------
% Tycho's SNR
% -----------
\subsection{Tycho's SNR}
Why Tycho's supernova remnant (hereafter, Tycho)?

Like SN 1006, Tycho has well defined synchrotron rims associated with expansion
into a low-density ISM \note[Aaron]{justification: high density ISM would
prevent the forward shock from running ahead of the thermal ejecta?}.
\citet{williams2013} favor mean pre-shock ISM density $\abt 0.2 \unit{cm^{-3}}$
from \textit{Spitzer} observations of shocked ISM dust emission,
\note[Aaron]{is this proton or electron density?  Or are they equal pre-shock?
Text mentions $n_e = 1.2 n_p$ \emph{post}-shock.}
consistent with Tycho's X-ray expansion \citep{katsuda2010}.
Compare w/ SN 1006 pre-shock density $n_p \abt 0.15$--$0.3 \unit{cm^{-3}}$
\citep{raymond2007, heng2007, winkler2013}.  \note[Aaron]{ISM gradients?}

Like all historical SNe, Tycho is close enough that we
can spatially resolve these rims with \Chandra and say something useful.

Previous estimates of Tycho fields/diffusion (something similar to Sean's table
for SN 1006?).  CR acceleration.

% -------------
% Paper roadmap
% -------------
\subsection{Our work (paper roadmap)}

We make measurements to distinguish between the two end member scenarios.
Our procedure, in both measurement and rim width modeling, follows that of
\citet{ressler2014} (hereafter, \citetalias{ressler2014}) with only slight
modifications.
We first select regions around Tycho's forward shock for analysis, measure
rim widths, and verify that rim spectra are free of thermal line emission.
Using two models for particle transport, we fit measured widths...

We discuss the implications of our fits and models for magnetic shock
amplification (lending credence to previous estimates, in disfavoring magnetic
field amplification), and discuss particle diffusion/acceleration at the shock.

Any further results (constraints on precursors, etc).

Consequences, implications, why is this worthwhile?

% =============================
% Transport models, observables
% =============================
\section{Transport models}

We first briefly review the models we consider for particle transport; a fuller
exposition is given by \citetalias{ressler2014}.

Just present the governing transport equations.  From:
\[
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\]
we obtain (1-D time-independent flow, neglect compressible flow?!,
space-independent diffusion coefficient):
\[
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C
\]
and by selection of the source/sink term $C$ we obtain either a
simplified model:
\begin{equation} \label{eq:simp-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
where this is equation (6) of \citetalias{ressler2014}; we also look at
\begin{equation} \label{eq:full-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citetalias{ressler2014}.

@@

@@

% ============
% Observations
% ============
\section{Observations}

% TODO go through and double check tenses.
\note[Aaron]{inconsistent present/past tense usage}
We measured synchrotron rim widths from an archival \Chandra
ACIS-I observation of Tycho
(RA: 00\tsup{h}25\tsup{m}19\fs0, dec: +64\arcdeg08\arcmin10\farcs0; J2000)
between 2009 Apr 11 and 2009 May 5 (PI: John P. Hughes;
\dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs: 10093--10097},
\dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}).
The total exposure time was $734 \unit{ks}$.
Level 1 \Chandra data were reprocessed with CIAO 4.6 and CALDB 4.6.1.1 and kept
unbinned with ACIS spatial resolution $0.492\arcsec$.
Merged and corrected events were divided into five energy bands:
0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV;
we excluded 1.7--2 keV counts to avoid \ion{Si}{13} (He$\alpha$) line
emission, prevalent in the remnant's thermal ejecta, which could contaminate
our nonthermal profile measurements.

We selected 13 regions in 5 distinct filaments around Tycho's shock
(Figure~\ref{fig:snr}) based on the following criteria:
(1) filaments should be singular and localized; multiple filaments must not
overlap or completely overlap (rules out parts of NE limb);
(2) filaments should have clear FWHMs in all bands, compared to background
signal or downstream thermal emission (rules out some faint southern wisps);
(3) filaments should be clear of spatial plumes of thermal ejecta in \Chandra
images; this rules out, e.g., areas of strong nonthermal and thermal emission
on Tycho's eastern limb.

\begin{figure}
    %\plotone{figures/f0-snr.pdf}
    \centering
    \includegraphics[width=0.35\textwidth]{figures/f0-snr.pdf}
    \caption{RGB image of Tycho with region selections overlaid.  Bands are
    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).
    \note[Aaron]{Temporary figure; regions need re-numbering.}}
    \label{fig:snr}
\end{figure}

Discuss point-spread function if that may be a point of contention.
Show that it is not a problem for us (simply say that all rims are at
least ~1 arcsec and hence are spatially resolved? Compare,
\citet{bamba2005-hist} measured upstream/downstream scale widths separately?)

% --------------------------
% FWHM measurement procedure
% --------------------------
\subsection{Filament width measurements}

We obtained radial intensity profiles by integrating along the shock in each
region.  Intensity profiles peak sharply at/behind the shock, demarcating our
thin rims, \note[Aaron]{abt 2--3 arcsec; measure this or report $w_u$?}
and then fall off until thermal emission from ejecta picks up at Tycho's
``contact discontinuity'' \citep{warren2005}.

We fit rim profiles, obtained by integrating intensity along the shock in each
region, to a piecewise two-exponential model:
\begin{equation} \label{eq:prof}
    h(x) =
    \begin{cases}
        A_u \exp \left(\frac{x_0 - x}{w_u}\right) + C_u, &x \geq x_0 \\
        A_d \exp \left(\frac{x - x_0}{w_d}\right) + C_d, &x < x_0
    \end{cases}
\end{equation}
where $h(x)$ is profile height and $x$ is radial distance from remnant center.
The rim model, which we emphasize is strictly empirical, has 6 free parameters
$A_u, x_0, w_u, w_d, C_u, C_d$ with $A_d = A_u + (C_u - C_d)$ enforcing
continuity at $x=x_0$. Our model is similar to that of \citet{bamba2003,
bamba2005-hist} and differs slightly from that of \citetalias{ressler2014}.
To fit only the nonthermal rim in each intensity profile, we smoothed profiles
with a 21-point ($\abt 10\arcsec$) Hanning window and bounded the fit
domain at the first local data minimum downstream of rim peak; the fit domain
extends upstream to the region's outer edge.

From the fitted profiles we extracted a full width at half maximum (FWHM) for
each region and each energy band.
\note[Aaron]{We did NOT subtract out $\min(C_u, C_d)$ before measuring FWHM
(fix this?).  May mention effect of using slightly different models for FWHMs}
We could not resolve a FWHM in regions 2, 6, 8, 9, and 11 \note[Aaron]{KEEP
UPDATED} at 0.7--1 keV (Table~\ref{tab:flmt2} \note[Aaron]{UPDATE depending on
how we present/tabulate FWHMs}); in these regions, the downstream FWHM bound
would extend outside the fit domain.  We were able to resolve FWHMs for all
regions at higher energy bands (1--7 keV).

To estimate FWHM uncertainties, we horizontally stretched each best-fit
profile by mapping radial coordinate $x$ to
$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x))$ with $\xi$ an arbitrary stretching
parameter; this yields a new profile $h'(x) = h(x'(x))$.
We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7,
yielding confidence limits on our measured FWHMs.

% ----------------
% Filament spectra
% ----------------
\subsection{Filament spectra}

We extracted and fitted spectra for all regions to confirm that our rim width
measurements are not contaminated by thermal line emission.
We divided each region into an upstream and downstream band.  The upstream band
is the smallest sub-region containing FWHM bounds from all energy bands.
The downstream band extends from the back of the rim (where the upstream band
ends) to the rim model fit's (equation~\eqref{eq:prof}) downstream limit.
Figure~\ref{fig:spec} plots an example profile (Region 1, 4.5--7 keV) with the
downstream/upstream selections highlighted in light blue/gray respectively.
We fitted spectra from each region to an absorbed power law between $0.5$ and $7$
keV in XSPEC.

TODO?! We also fit the spectra to absorbed power law models with 1 and 2
additional Gaussian components for \ion{Si}{13} and \ion{S}{15} He$\alpha$
lines at $\abt 1.8$, $2.4$ keV.  We compute some equivalent width, or compare
the goodness-of-fit with and without the additional lines, to rule out the
presence of a line (but, cf. \citet{protassov2002} on line detection
statistics!).

% -------------
% Model fitting
% -------------
\subsection{Filament model fitting}

We fitted the two transport models given by Equations~\eqref{eq:simp-mod} and
\eqref{eq:full-mod} to the measured data.  Here we present only the full
model (equation~\eqref{eq:full-mod}) fits.  \note[Aaron]{Could we present the
full model alone, given that the numbers / qualitative trends for both models
are fairly similar?  In \citetalias{ressler2014} Sean used the simple model to
build intuition and gain physical insight, to great effect.  But, will we need
that here?}

Explain why we are fixing $\mu$.
Explain why we also give results with $\eta_2$ fixed at $1$.

>>>>

%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
% \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
% \documentclass[iop, apj, numberedappendix]{emulateapj}

@@

\usepackage{amsmath}  % amsthm, amssymb
% \usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
\usepackage{booktabs}
%\usepackage[labelfont=bf, labelsep=period]{caption}  % Custom float captions
%\usepackage{pdflscape}  % rotate pages (Texlive)
\usepackage{hyperref}

\newcommand*{\mt}{\mathrm}
\newcommand*{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
\newcommand*{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
\newcommand*{\ptl}{\partial}
\newcommand*{\del}{\nabla}

% This paper
\newcommand*{\tsup}{\textsuperscript}
\newcommand*{\Chandra}{\textit{Chandra}\ }
\newcommand*\mean[1]{\bar{#1}}
\newcommand*{\tsynch}{\tau_{\mt{synch}}}
\defcitealias{ressler2014}{R14}

@@

\title{Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent}

@@

\begin{abstract}
\note[Aaron]{Copy pasted from NASA abstract, not reviewed} Young supernova
remnants may exhibit thin (~1--10\% of shock radius) X-ray rims of synchrotron
radiation from forward shock-accelerated electrons that travel downstream of
the shock and quickly cease to radiate. Rim widths limited by radiative energy
losses should decrease with energy and require magnetic field amplification
$10$--$100\times$ that expected from adiabatic shock compression.  Damped
magnetic fields behind rims may produce thin rims without strong field
amplification but require energy-independent rim widths. We measured rim widths
around Tycho's supernova remnant in 5 energy bands using a 750 ks \Chandra
observation. Rims narrow with increasing energy, favoring loss-limited
radiation over magnetic damping. Observed widths are best fit by electron
transport models requiring amplified magnetic fields $\abt0.1$--$1$ mG and
particle diffusion $\abt1$--$10\times$ Bohm values, consistent with prior work
on SN 1006. Inferred magnetic fields, diffusion coefficients, and
diffusion-energy scaling may constrain models for cosmic ray acceleration in
supernova remnants and plasma turbulence in astrophysical shocks.
\end{abstract}

@@

\note[Aaron]{this first draft of intro structure is mostly set (in terms of
material, number of paragraphs).}

% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
Forward shock accelerated ISM/CSM particles in young supernova remnants emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream \citep{koyama1995, reynolds1996}, producing a shell-like
morphology with bright X-ray and radio rims/filaments due to line-of-sight
projection (hereafter, thin rims).
Seminal observations \& interpretations of these filaments, interpretation in
context of DSA.
People (such as the authors of this manuscript) are trying to model these
filaments and figure out what's going on.
Why do we care about these models?  They tell us something about what happens
behind the shock, and perhaps what's going on at the shock.  We get at the
plasma turbulence, magnetic field turbulence and structure, electron injection.
Applications to: cosmic ray acceleration, turbulent field amplification, (note
assumptions in re proton/electron spectra).  Cut-off energy of injected
electrons?  Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
AGN jets, galaxy clusters \citep{van-weeren2010}, cosmological shocks?!
\citep{miniati2000, ryu2008}, other cool stuff.  See relevant reviews
\citep{blandford1987}.

% What makes these shocks?
The widths of these X-ray rims are thought to be controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  At the shock, high energy electrons efficiently radiate harder
synchrotron X-ray photons; as they are transported away from the shock, they
radiate at lower energies and lose energy more slowly.  The transport process
is driven by both bulk plasma advection away from the shock at downstream
velocity $v_d = v_s / r$, where $v_s$ is shock velocity and $r$ the compression
ratio, and diffusion ... (driven by collisionless particle interaction,
magnetic field turbulence, ????? fill in details) with respect to bulk
advection.  Energy-dependent diffusion (e.g., diffusion coefficient $D \propto
E$ for Bohm diffusion) allows higher energy electrons to diffuse further
upstream or downstream than would be expected from pure advection; in
particular, diffusion upstream of the shock may give rise to a shock precursor
\citep[e.g.,][]{ghavamian2000, wagner2009, laming2014}.  Finally, the magnetic
field strength may be quickly damped behind the shock, so that electrons may
not radiate as efficiently and thin rims would reflect the spatial structure of
the field, rather than efficient particle acceleration (and losses) and/or
efficient synchrotron cooling \citep{pohl2005}.  \note[Aaron]{I need to read up
on particle transport, diffusion, plasma physics!}

% Energy dependence.
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  Loss-limited rims should scale as $w \propto
\nu^{-1/2}$.  Diffusion weakens this energy dependence by smearing out rims at
all energies (even for energy-independent diffusion), yielding a slower
drop-off in rim widths when diffusion dominates.  Magnetic damping, at a
length scale where it may be considered a relevant control on rim widths (i.e.,
length scale comparable to filament width) predicts energy-independent rim
widths -- intuitively, if the magnetic field turns off, synchrotron radiation
turns off regardless of electron energy.  \citet{ressler2014} give a much
fuller exposition of the relative effects of advection, diffusion, and magnetic
field damping.

% Which one is right?
Previous measurements of basic observables \citep[e.g.,][]{bamba2003,
bamba2005-hist, bamba2005-vela, parizot2006} and consequences.  Conclusion that
magnetic fields are amplified according to loss-limited model.  How could this
be plausible?  There are possible explanations -- field amplification from
plasma instabilities, evidence for stronger compression ratios?
\citep{blondin2001}.  Numerical simulations and theory on this matter
accounting for streaming instabilities, CR escape / energy losses, MHD
equations, all sorts of things I can't keep track of.  But, magnetic damping
model offers a tantalizing alternate explanation, and has not been tested.
Equivocal results by \citet{araya2010} for Cas A.
\citet{rettig2012} proposed discriminating based on filament spectra -- the
expectation is that damped spectra are softer, loss-limited harder.
\citet{ressler2014} developed the idea of investigating energy dependence and
found rim narrowing in the remnant of SN 1006, strongly favoring a loss-limited
model.

% Why Tycho's SNR
To test these models, we turn to the filaments of Tycho's supernova remnant
(hereafter, Tycho).
Like all historical SNe, Tycho is close enough that we can spatially
resolve these rims with \Chandra and say something useful.  Like SN 1006, Tycho
has well defined synchrotron rims associated with expansion into a low-density
ISM.  \citet{williams2013} favor mean pre-shock ISM density $\abt 0.1$--$0.2
\unit{cm^{-3}}$ from \textit{Spitzer} observations of shocked ISM dust
emission, consistent with Tycho's X-ray expansion rate \citep{katsuda2010}; SN
1006, by comparison, has pre-shock density $\abt 0.01$--$0.1 \unit{cm^{-3}}$ at
its nonthermal NE, SW limbs \citep{acero2007}.
\note[Aaron]{More disjointed}
Mention molecular cloud interaction \citep{reynoso1999}? Maybe below in region
selection as well.
Previous estimates of Tycho fields/diffusion (something similar to Sean's table
for SN 1006?).  CR acceleration (aside: \citet{eriksen2011}) evidence in Tycho,
if relevant.

% Paper roadmap
\note[Aaron]{roadmap}
We measure Tycho's rim widths, following the work of \citet{ressler2014}
(hereafter, \citetalias{ressler2014}) in the remnant of SN 1006.  
We make measurements to distinguish between two main scenarios
(explain how diffusion/advection competition come into this).
Our procedure, in both measurement and rim width modeling, follows that of
\citetalias{ressler2014} with only slight modifications.
We first select regions around Tycho's forward shock for analysis, measure
rim widths, and verify that rim spectra are free of thermal line emission.
Using two models for particle transport, we fit measured widths...
We discuss the implications of our fits and models for magnetic shock
amplification (lending credence to previous estimates, in disfavoring magnetic
field amplification), and discuss particle diffusion/acceleration at the shock.
Any further misc. applications (constraints on precursors, etc).

% =============================
% Transport models, observables
% =============================
\section{Electron transport models}\label{sec:transport}

We briefly review relevant particle transport models that we use to fit our
measurements; a fuller review and exposition is given by \citetalias{ressler2014}.
\note[Aaron]{is it necessary to give Sean's equation numbers?  How many of the
derived equations should we give?}  In particular, the transport models 
account for both advection and diffusion simultaneously, as opposed to
considering the lengthscales separately with advection dominating below a
critical energy and diffusion, above
\citep{bamba2003, vink2003, yamazaki2004, bamba2005-hist}
\note[Aaron]{clarify, be more specific}.
The effects of varying various parameters, especially in regards to filament
energy dependence, are explored in detail by \citetalias{ressler2014}.

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
%      notation is being used)
\note[Aaron]{Double check against Rettig/Pohl.  Variable definitions will be
added when equations/exposition is closer to final state.}
The electron distribution which gives rise to the observed synchrotron
radiation is injected at the forward shock and transported by advection
and plasma diffusion, following the advection-diffusion equation:
\[
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\]
By considering only steady-state transport and some other assumptions
(1-D flow (did we neglect the spherical coord terms?), neglect compressible flow?!,
space-independent diffusion coefficient):
\[
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\]
The source/sink term $C$ reflects assumptions about the injected electron
energy spectrum and its time/space evolution.
A first approximation is to treat electrons as having constant energy, but
dumping energy catastrophically after a synchrotron timescale
$\tsynch$ \note[Aaron]{define this -- either Section~\ref{sec:transport} before jumping into
transport models, or in the intro}, yielding:
\begin{equation} \label{eq:simp-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
where this is equation (5) of \citetalias{ressler2014}.
Equation~\eqref{eq:simp-mod} has a convenient analytic solution (note that
neglecting diffusion, this is $\ptl f/\ptl x \propto -f/(\tsynch v_d)$.
A more advanced model is given by accounting for continuous radiation energy
losses while electrons are transported downstream, given as:
\begin{equation} \label{eq:full-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citetalias{ressler2014}.

@@

\subsection{Energy dependent widths, diffusion}

Bohm diffusion: $D(E) = \eta C_d E / B$. Generalized diffusion writen as:
\[
    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
\]
Explain the use of fiducial energy -- this makes sense and eases discussion,
but linking $E_h$ and $\eta_2$ to $\eta$ and plain Bohm diffusion seems a bit
murky.

For the simple model, we have equation (6) of \citetalias{ressler2014}:
\begin{equation} \label{eq:simp-width}
    a = \frac{2 D / v_d}{ \sqrt{ 1 + \frac{4D}{v_d^2 \tau_{\mt{synch}}}} - 1}
\end{equation}
which we relate to full width half max by projection factor $\beta = 4.6$
so that $w = \beta a$, assuming (1) electron distribution exponential in radial
coordinate $x$, and (2) spherical source \note[Aaron]{shell?}
\citep{ballet2006}.

For the full model (equation~\eqref{eq:full-mod}), we numerically solve for
electron distribution $f(E,x)$ using solutions due to \citet{lerche1980} and
\citet{rettig2012}; DETAILS.
Ultimately, we integrate numerically computed electron distributions $f(E,x)$
over energy to obtain synchrotron emissivity as
\[
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\]
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is the one-particle synchrotron
emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight yields
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.

\subsection{Tycho parameters}

Give numbers ($v_s$, $v_d$, $r_s$, etc.).  Give a definition of the cut-off
energy following Rettig and Pohl (again cite Sean's paper).
We use an electron spectrum cut-off energy of:
\begin{align*}
    E_{\mt{cut}} =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \\
        &\times \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
        \left[
            \frac{E_h^{\mu - 1}}{\eta}
        \right]^{1 / (1 + \mu)}
\end{align*}
which is equation~(19) of \citetalias{ressler2014}.
\note[Aaron]{This differs from Sean's presentation -- I drew this from the
Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
$E_h$ ?!  Come back to this shortly.}

@@

% ============
% Observations
% ============
\section{Observations}
\label{sec:observations}

% TODO go through and double check tenses.
We measured synchrotron rim full widths at half maximum (FWHMs) from an
archival \Chandra ACIS-I observation of Tycho
(RA: 00\tsup{h}25\tsup{m}19\fs0, dec: +64\arcdeg08\arcmin10\farcs0; J2000)
between 2009 Apr 11 and 2009 May 5 (PI: John P. Hughes;
\dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs: 10093--10097},
\dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}).
The total exposure time was $734 \unit{ks}$.
Level 1 \Chandra data were reprocessed with CIAO 4.6 and CALDB 4.6.1.1 and kept
unbinned with ACIS spatial resolution $0.492\arcsec$.
Merged and corrected events were divided into five energy bands:
0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
We excluded 1.7--2 keV energy range to avoid the \ion{Si}{13} (He$\alpha$)
emission line at 1.85 keV, prevalent in the remnant's thermal ejecta, which
\remove[Brian]{could} \remove[Aaron]{would} \add[Aaron]{may}
\note[Aaron]{since some profiles are practically uncontaminated?}
contaminate our nonthermal profile measurements.

We selected 13 regions in 5 distinct filaments around Tycho's shock
(Figure~\ref{fig:snr}) based on the following criteria:
(1) filaments should be clear of spatial plumes of thermal ejecta in \Chandra
images; this rules out, e.g., areas of strong thermal emission on Tycho's eastern limb.
(2) filaments should be singular and localized; that is, multiple filaments
should either not overlap or completely overlap (rules out parts of NE limb);
(3) filaments should have clear FWHMs bands; i.e., a peak should be evident
above the background signal or downstream thermal emission (rules out some
faint southern wisps) \note[Aaron]{wishy-washy qualitative}.

\begin{figure}
    \centering
    %\plotone{figures/f0-snr.pdf}
    \includegraphics[width=0.35\textwidth]{figures/f0-snr.pdf}
    \caption{RGB image of Tycho with region selections overlaid.  Bands are
    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).
    \note[Aaron]{Temporary figure; regions need re-numbering.}
    \note[Aaron]{We could show the spectrum extraction regions on here too?
    Maybe too cluttered.}}
    \label{fig:snr}
\end{figure}

All measured rim widths are at least $\abt 1\arcsec$ and hence are resolved by
\textit{Chandra}'s point-spread function.

% ----------------
% Filament spectra
% ----------------
\subsection{Filament spectra}
\label{sec:spec}

We extracted spectra for all regions to check that rim width measurements are
not affected by contaminating thermal line emission.  In each region, we
selected upstream and downstream sections \note[Aaron]{any better word than
`section'?} from which to extract spectra.
The upstream section is the smallest sub-region that contains the measured FWHM
bounds from all energy bands (see Section~\ref{sec:fwhms}); i.e., this region
captures the thin rim.
The downstream section extends from the back of the rim (where the upstream
section ends) to the rim model fit's
(equation~\eqref{eq:prof}) downstream limit.
Figure~\ref{fig:spec} plots an example profile (4.5--7 keV) with the
downstream and upstream sections highlighted; the dividing line is set at the
\textbf{???--???} energy band's downstream FWHM limit (see Figure~\ref{fig:profiles}).
Background spectra were extracted from circular regions around the remnant's
exterior \note[Aaron]{give size in arcsec?}; each region's spectra used the
closest background region's spectrum \note[Aaron]{a bit awkward}.

% TODO must match fig:profiles!  Keep both figures' region numbers updated and
% consistent.
\begin{figure}
    \plotone{figures/f0-spec.pdf}
    \caption{Example spectra and fits from Region 1. Left: example profile
    ($4.5$--$7 \unit{keV}$) with highlighted downstream (blue) and upstream
    (grey) sections. These sections are fixed for Region 1, regardless of
    energy band (to be absolutely clear).  Middle: downstream spectrum with
    fitted absorbed power law; Si and S lines at $1.85$, $2.45 \unit{keV}$ are
    clearly visible.  Right: upstream spectrum with fitted absorbed power law
    shows that the thin rim is not contaminated by line emission.}
    \label{fig:spec}
\end{figure}

We fit $0.5$--$7 \unit{keV}$ spectra from each region's upstream and downstream
sections to an absorbed power law model (XSPEC 12.8.1, \texttt{phabs*po}) with
spectral index $n$, hydrogen column density $n_H$, and a normalization as free
parameters.  Table~\ref{tab:spec} lists best fit parameters and reduced
$\chi^2$s for all regions.  Spectra from thin rims (upstream sections) are
well-fit by the power law model alone; spectra from sections downstream of the
rims are generally poorly-fit, reflecting thermal contamination primarily from
\ion{Si}{13} and \ion{S}{15} He$\alpha$ line emission at $1.85$ and $2.45$ keV.
Although most downstream spectra show thermal contamination, some regions
(e.g., 3, 4 on Tycho's northwestern limb) are reasonably well-fit by an
absorbed power law as well due to a larger distance between the forward shock
and contact discontinuity.
Upstream spectra fits spectral indices between $2.5$--$3$ are consistent with
synchrotron radiation spectra for ???? population of electrons
\note[Aaron]{citation for e- distr. indices?}. Best fit column densities have
range ($0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$) consistent with previous
fits to Tycho's nonthermal rims \citep{hwang2002} but somewhat larger than
values reported from radio and optical? HI absorption line measurements
($\abt0.5 \times 10^{22}$ in radio \citep{albinson1986} per \citet{hwang2002};
$\abt0.35 \times 10^{22}$ by \citet{kothes2004}, $\abt 0.4 \times 10^{22}$ from
extinction--gas ratio (references in \citet{black1984})...).
% TODO keep stated ranges of spectral indices, column densities up to date

\note[Aaron]{On rob's suggestion of fitting thermal model -- can we get away
with just fitting line emission and constraining from there? or is the
whole NEI apparatus needed.  If we add thermal components -- report spectral
indices and show better fit / spectral softening (confirmation)?}

% TODO short script to build table from saved spectra fits
% TODO keep region numbers updated (discussion of good/bad downstream spectra)
\begin{table}
    \scriptsize
    \centering
    \caption{Absorbed power law fit parameters for all regions' upstream and
    downstream spectra.  The reduced $\chi^2$ values for upstream spectrum fits
    are consistent with a lack of thermal emission, whereas downstream spectra
    are often poorly-fit by an absorbed power law due to line
    emission (e.g., Figure~\ref{fig:spec}).\label{tab:spec}}
    \input{tab-spec.tex}
\end{table}
